Monte Carlo for all parameters

### 2024-07-25 Draft/Draft.Rmd
Better version of Two_var
More global MC and function for local variables
Obviously a pb with variances

## Tessellation

@@

## Draft

@@

## Circle

@@

## Draft for bootstrap

@@

### Complexity

@@

### A first package

@@

### Another package

@@

# Grid for trees

@@

# Bootstrap

@@

# Alarm / beep / message when it finishes running

@@

>>>>

## Tessellation ----------

@@

## Draft ----------

@@

## Circle ----------

@@

## Draft for bootstrap ----------

@@

### Complexity ----------

@@

### A first package ----------

@@

### Another package ----------

@@

# Grid for trees ----------

@@

# Bootstrap ----------

@@

# Alarm / beep / message when it finishes running ----------

@@

# Variance ----------

```{r}
# Unbiased variance

# Test
test <- c(1,2,3,5)
var(test) # 2.916667

varbis <- function(x){

# Print LaTeX code as output of R code (failure) ----------

```{r}
print("* $H_o = `r 1 + 1`$")
b0 = "$\\beta_0$"
m3 = "$m^3$"
cat("thing:",m3)
cat("thing:",`b0`)
```

```{r}
print(bquote(m^2))
```

# Small examples for MC_all.Rmd ----------

```{r}
# Small test

res_MC <- MonteCarlo(100, 200)

end.time <- Sys.time()
time.taken <- end.time - start.time

time.taken
```

```{r}
# mean(as.vector(t(res_MC$Estimators[1,])))

cat("95% confidence interval using the percentile method: 
      [", res_MC$`Confidence Intervals`$Percentile[1,1], ";", res_MC$`Confidence Intervals`$Percentile[2,1], "]\n" )

# cat("95% confidence interval using the reverse percentile method: 
#       [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]\n" )
```

```{r}
# Small test

res_MC_boot <- MC_boot(100, 200, 100)

end.time <- Sys.time()
time.taken <- end.time - start.time

time.taken
```

### 2024-07-25 MC_all.Rmd
Obviously a pb with variances

```{r}
# Importing the database with the artificial forest
all_trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
# To get closer to the NFI process, trees whose circumference is under 23.5 cm are not considered
trees <- trees[(pi*trees$d130 > 23.5),]
```

@@

  return(list(`Local Variables` = MC_df, Estimations = MC_est, Variances = MC_var, `Confidence Intervals` = all_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimators: 3 estimators (number, volume, ratio volume / number) for each sample
  # Variances: Monte Carlo variance for each of the totals / ratio
  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
}
```

```{r}
# Small test

start.time <- Sys.time()

res_MC <- MonteCarlo(100, 200)

```{r}
# mean(as.vector(t(res_MC$Estimators[1,])))

cat("95% confidence interval using the percentile method: 
      [", res_MC$`Confidence Intervals`$Percentile[1,1], ";", res_MC$`Confidence Intervals`$Percentile[2,1], "]\n" )

# cat("95% confidence interval using the reverse percentile method: 
#       [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]\n" )
```

@@

```{r}
# Small test

start.time <- Sys.time()

res_MC_boot <- MC_boot(100, 200, 100)

@@

```{r}
cat("Monte Carlo means of estimators: \n - for the number of trees:", mean(as.vector(t(res1$Estimators[1,]))), "\n - for the volume of trees:", mean(as.vector(t(res1$Estimators[2,]))), "\n - for the ratio volume / number of trees:", mean(as.vector(t(res1$Estimators[3,]))))
# Example:
```

```{r}
cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[2], "\n - for the ratio volume / number of trees:", res1$Variances[3])
# Example:
```

```{r}
cat("95% confidence intervals using the normal method: 
    \n - for the number of trees: [", res1$`Confidence Intervals`$Normal[1,1], ";", res1$`Confidence Intervals`$Normal[2,1], 
    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Normal[1,2], ";", res1$`Confidence Intervals`$Normal[2,2], 
    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Normal[1,3], ";", res1$`Confidence Intervals`$Normal[2,3],
    "]")
```

```{r}
cat("95% confidence intervals using the percentile method: 
    \n - for the number of trees: [", res1$`Confidence Intervals`$Percentile[1,1], ";", res1$`Confidence Intervals`$Percentile[2,1], 
    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Percentile[1,2], ";", res1$`Confidence Intervals`$Percentile[2,2], 
    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Percentile[1,3], ";", res1$`Confidence Intervals`$Percentile[2,3],
    "]"
    )
```

```{r}
cat("95% confidence intervals using the reverse percentile method: 
    \n - for the number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,1], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,1], 
    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,2], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,2], 
    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,3], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,3],
    "]"
    )
```

@@

```{r}
# PROBLEM NOW: MEAN of variance for each estimation
# How to extract it without a loop? mapply with function made up

cat("Mean of the variance of bootstrap samples: \n - for the number of trees:", res2$Variances[1], "\n - for the volume of trees:", res2$Variances[2], "\n - for the ratio volume / number of trees:", res2$Variances[3])
# Example:
```

@@

```{r}
diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(res1$Variances[1], res2$Variances[1]), "%", "\n - for the volume of trees: ", diff_percent(res1$Variances[2], res2$Variances[2]), "\n - for the ratio volume / number of trees: ", diff_percent(res1$Variances[3], res2$Variances[3]), sep = "")
# Example:
```

>>>>

```{r}
# Importing the database with the artificial forest
all_trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
# To get closer to the NFI process, trees whose circumference is under 23.5 cm are not considered
trees <- all_trees[(pi*all_trees$d130 > 23.5),]
```

@@

  return(list(`Local Variables` = MC_df, Estimations = MC_est, Variances = MC_var, `Confidence Intervals` = all_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimations: 3 Estimations (number, volume, ratio volume / number) for each sample
  # Variances: Monte Carlo variance for each of the totals / ratio
  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
}
```

@@

@@

```{r}
cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(as.vector(t(res1$Estimations[1,]))), "\n - for the volume of trees:", mean(as.vector(t(res1$Estimations[2,]))), "\n - for the ratio volume / number of trees:", mean(as.vector(t(res1$Estimations[3,]))))

# Example:
# Monte Carlo means of estimations: 
#  - for the number of trees: 29299.58 
#  - for the volume of trees: 5418.03 
#  - for the ratio volume / number of trees: 0.1849162
```

```{r}
cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[2], "\n - for the ratio volume / number of trees:", res1$Variances[3])

# Example:
# Monte Carlo variances: 
#  - for the number of trees: 2531530 
#  - for the volume of trees: 96840.38 
#  - for the ratio volume / number of trees: 1.116039e-05
```

```{r}
cat("95% confidence intervals using the normal method:\n - for the number of trees: [", res1$`Confidence Intervals`$Normal[1,1], ";", res1$`Confidence Intervals`$Normal[2,1], 
    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Normal[1,2], ";", res1$`Confidence Intervals`$Normal[2,2], 
    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Normal[1,3], ";", res1$`Confidence Intervals`$Normal[2,3],
    "]")

# Example:
# 95% confidence intervals using the normal method: 
#  - for the number of trees: [ 25885.94 ; 32122.85 ]
#  - for the volume of trees: [ 4727.737 ; 5947.587 ]
#  - for the ratio volume / number of trees: [ 0.1774817 ; 0.1905771 ]
```

```{r}
cat("95% confidence intervals using the percentile method:\n - for the number of trees: [", res1$`Confidence Intervals`$Percentile[1,1], ";", res1$`Confidence Intervals`$Percentile[2,1], 
    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Percentile[1,2], ";", res1$`Confidence Intervals`$Percentile[2,2], 
    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Percentile[1,3], ";", res1$`Confidence Intervals`$Percentile[2,3],
    "]")

# Example:
# 95% confidence intervals using the percentile method: 
#  - for the number of trees: [ 26203.27 ; 32429.41 ]
#  - for the volume of trees: [ 4817.327 ; 6027.707 ]
#  - for the ratio volume / number of trees: [ 0.1786038 ; 0.1915195 ]
```

```{r}
cat("95% confidence intervals using the reverse percentile method:\n - for the number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,1], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,1], 
    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,2], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,2], 
    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,3], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,3],
    "]"
    )

# Example:
# 95% confidence intervals using the reverse percentile method:
#  - for the number of trees: [ 25579.38 ; 31805.52 ]
#  - for the volume of trees: [ 4647.617 ; 5857.997 ]
#  - for the ratio volume / number of trees: [ 0.1765393 ; 0.189455 ]
```

@@

```{r}
VAR_nb <- c()
for (elt in res2$Variances) {
  VAR_nb <- append(VAR_nb, elt$var_nb)
}

VAR_vol <- c()
for (elt in res2$Variances) {
  VAR_vol <- append(VAR_vol, elt$var_vol)
}

VAR_ratio <- c()
for (elt in res2$Variances) {
  VAR_ratio <- append(VAR_ratio, elt$var_ratio)
}
```

```{r}
cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(VAR_nb), "\n - for the volume of trees:", mean(VAR_vol), "\n - for the ratio volume / number of trees:", mean(VAR_ratio))

# Example:
# Mean of the variance of bootstrap samples:
#  - for the number of trees: 6.273237e+16 
#  - for the volume of trees: 98861.68 
#  - for the ratio volume / number of trees: 0.1741024
```

@@

```{r}
diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(res1$Variances[1], mean(VAR_nb)), "%", "\n - for the volume of trees: ", diff_percent(res1$Variances[2], mean(VAR_vol)), "%\n - for the ratio volume / number of trees: ", diff_percent(res1$Variances[3], mean(VAR_ratio)), "%", sep = "")

# Example:
# Difference between the two estimations of variance: 
#  - for the number of trees: 2.478042e+12%
#  - for the volume of trees: 2.087256%
#  - for the ratio volume / number of trees: 1559903%
```
